\LARGE \bf Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*

### 2015-11-17 submission/root.tex
rewrite .bib file & description for figure & minor changes

\begin{figure}[t!]
\centering
\includegraphics[width=3.2in]{fig1.eps}
\caption{
(1) The hand-eye and robot-world calibration problem formulated as AX=YB. (2) The hand-eye calibration problem formulated as AX=XB. Note: matrices $A$ and $B$ above have different physical meanings in the $AX=XB$ and $AX=YB$ problems. (The Universal Robot pictured above is owned by Prof. Emad Boctor of Johns Hopkins University).
}
\label{fig1}
\end{figure}

The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively. As shown in Fig.~\ref{fig1} part (2), $A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$. Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu \cite{Shiu1989} and Tsai \cite{Tsai1989} are the first to solve the $AX = XB$ sensor calibration problem. The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}. All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$. For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without a priori knowledge of the correspondence. These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.

Simultaneous estimation of the hand-eye and robot-world transformations has been viewed as the $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1} part (1), $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the end-effector to its fixed base. The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations. This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}. Simulatneous calibration %s
of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why a simultaneous solution for $X$ and $Y$ in the $\textbf{AX=YB}$ problem can be a challenging issue. Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014} which will not be discussed in detail here. In the above methods, the correspondence between $A$ and $B$ is known a priori. In this paper, we focus on one case of the $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.

@@

\begin{IEEEeqnarray}{l}\label{equ11}
\int log(M^{-1}H))f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
If $f_A(H)$ is given as in Eq.~\ref{equ8}, then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:

@@

Given $\{A_i\}$ with the cloud of frames ${A_{i}}$ clustering around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{Wang2008} as:

@@

The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly-focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{Wang2008}:

@@

The probabilistic method in this paper can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods. In the $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence. However, few of them considered the cases without correspondence. When data streams of ${A}$ and ${B}$ are shifted or asynchronous, most of these methods fail to give a valid solution. To further test the effectiveness of our method, we shift the data sequence of $\{A_i\}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of $\{B_i\}$. We augment other $AX=YB$ solvers with our probabilistic approach. In Li's method \cite{Li2010}, $X$ and $Y$ are solved for at the same time while Shah \cite{Shah2013} uses separable solutions to solve for $X$ and $Y$. In Fig.~\ref{fig5}, the correspondence between data streams is unknown and the errors on both rotations and translations are significant. After synchronizing the data streams by using the probabilistic method, Li and Shah's methods achieve the same level of performance as in the no-shift situation as shown in Fig.~\ref{fig6}.

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibIEEEfull}
%\begin{thebibliography}{1}
%
%
%\end{thebibliography}

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=3.2in]{fig1.eps}
\caption{
(1) The hand-eye and robot-world calibration problem formulated as AX=YB. (2) The hand-eye calibration problem formulated as AX=XB. Note: matrices $A$ and $B$ above have different physical meanings in the $AX=XB$ and $AX=YB$ problems. (The Universal Robot pictured above is owned by Prof. Emad Boctor of Johns Hopkins University). Note: the $A$ and $B$ in the above two problems have different physical meanings. One is the absolute transformation and the other is relative transformation as can be seen in the figures. 
}
\label{fig1}
\end{figure}

The hand-eye calibration problem can be modelled as $\textbf{AX = XB}$, where $A$ and $B$ are the homogeneous transformation matrices describing the relative motions of the end-effector and the  sensor respectively. As shown in Fig.~\ref{fig1} part (2), $A = A^{i}(A^{i+1})^{-1}$ and  $B = (B^{i})^{-1}B^{i+1}$. Given multiple pairs of $(A_i,B_i)$ with correspondence (note that $(A_i,B_i)$ are the relative transformations obtained from the raw data), many deterministic methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu \cite{shiu1989calibration} and Tsai \cite{tsai1989new} are the first to solve the $AX = XB$ sensor calibration problem. The other methods include but are not limited to the quaternion, dual quaternion, screw theory, Lie group theory,motor algebra, convex optimization and gradient descent methods \cite{wang1992extrinsic,park1994robot,horaud1995hand,daniilidis1999hand,bayro2000motor,fassi2005hand,zhao2011hand,ackerman2014online}. All of the methods above assume a priori knowledge of the exact correspondence between $A_i$ and $B_i$. For data streams $\{A_i\}$ and $\{B_j\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without a priori knowledge of the correspondence. These methods assume that there are some corresponding pairs of data in the streams of the $\{A_i\}$ and $\{B_j\}$; however,  the exact correspondence is unknown \cite{ackerman2013probabilistic, ackerman2014online ,ackerman2014information}.

Simultaneous estimation of the hand-eye and robot-world transformations has been viewed as the $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1} part (1), $Y$ is the transformation from the robot base to the world frame, $A$ denotes the pose of the sensor in the world frame and $B$ is the transformation from the end-effector to its fixed base. The $A$ and $B$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ where the former uses absolute transformations and the latter uses relative transformations. This problem has been solved by many different methods such as the Kronecker product, quaternion, dual quaternion, and nonlinear optimization methods \cite{zhuang1994simultaneous,dornaika1998simultaneous,hirsh2001iterative, ernst2012non,strobl2006optimal,li2010simultaneous,shah2013solving,heller2014hand}. Simulatneous calibration %s
of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_i\}$ and $\{B_j\}$, which is not the case in the real world, and this is why a simultaneous solution for $X$ and $Y$ in the $\textbf{AX=YB}$ problem can be a challenging issue. Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange\textcolor{blue}{,} and robot-robot transformations, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{wang2014towards} which will not be discussed in detail here. In the above methods, the correspondence between $A$ and $B$ is known a priori. In this paper, we focus on one case of the $\textbf{AX=YB}$ problem where there is no a priori knowledge of the correspondence between the data streams.

@@

\begin{IEEEeqnarray}{l}\label{equ11}
\int log(M^{-1}H))f(H)dH = \mathbb{O}  \IEEEyessubnumber
\\*
\Sigma = \int log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}
where the explicit expression of the matrix logarithm $log(H)$ along with its vectorized form $log^{\vee}(H)$ are given in \cite{chirikjian2011stochastic}.
If $f_A(H)$ is given as in Eq.~(\ref{equ8}), then the corresponding discrete version of the mean $M_A$ and covariance $\Sigma_A$ will be:

@@

Given $\{A_i\}$ with the cloud of frames ${A_{i}}$ clustering around $M_{A}$, an iterative formula can be used for computing $M_{A}$ \cite{wang2008nonparametric} as:

@@

The mean and covariance for the convolution $(f_{1} \ast f_{2})(g)$ of two highly-focused functions $f_{1}$ and $f_{2}$ are calculated as in \cite{wang2008nonparametric}:

@@

The probabilistic method in this paper can recover the correspondence between shifted data streams, which is useful for other sensor calibration methods. In the $AX=YB$ problem, there have been many calibration methods developed for solving $X$ and $Y$ given data streams with correspondence. However, few of them considered the cases without correspondence. When data streams of ${A}$ and ${B}$ are shifted or asynchronous, most of these methods fail to give a valid solution. To further test the effectiveness of our method, we shift the data sequence of $\{A_i\}$ by $n=0,1,2,3,4,5$ with respect to the data sequence of $\{B_i\}$. We augment other $AX=YB$ solvers with our probabilistic approach. In Li's method \cite{li2010simultaneous}, $X$ and $Y$ are solved for at the same time while Shah \cite{shah2013solving} uses separable solutions to solve for $X$ and $Y$. In Fig.~\ref{fig5}, the correspondence between data streams is unknown and the errors on both rotations and translations are significant. After synchronizing the data streams by using the probabilistic method, Li and Shah's methods achieve the same level of performance as in the no-shift situation as shown in Fig.~\ref{fig6}.

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,root}
%\begin{thebibliography}{1}
%
%
%\end{thebibliography}
